Endogenous Politics and \\ the Design of Trade Institutions

### 2018-02-25 to-do.tex
update to-do list
add ideas from IER referee reports to to-do.tex

@@

\newpage
\begin{center}
\textbf{\large{For Later}}
\end{center}

>>>>

\section{From IER Referee Reports}
\begin{itemize}
	\item Is there a proposition to support each of my main points?
	\item Make results more formal
		\begin{itemize}
			\item explicitly provide mappings from exogenous parameter regions to predictions about endogenous variables. For example, Proposition 2 simply indicates that a certain prediction ``may'' emerge without providing a detailed formal characterization.
		\end{itemize}
	\item Result 2 is interesting but not new
	\item Clarifying points
		\begin{itemize}
			\item I would recommend saying on p. 7 what it means to “form a trade agreement.” I believe at this point in the paper the meaning is a tariff binding of some kind.
			\item I would recommend formally defining the Wx function on p. 9. This is used often in the sequel, and I was unclear as to whether this function includes the lobbying cost “-e” that is found in expression (1).
			\item In expression (3) on p. 10, it would be helpful to discuss the tariff function that is embedded in the profit function. Is this the “trade agreement”? By using this function, are we assuming that political pressure is observed here? I was a little uncertain as to exactly what was being represented here.
			\item In expression (5) on p. 11, where is the expectation over s and s*? Isn’t the trade agreement formed in anticipation of possible economic shocks? Since political pressure is privately observed, should the reader understand this as a complete-information benchmark of some kind? If so, is this the same “trade agreement” tariff that was mentioned previously?
			\item On p. 14, rigid tariffs are defined as corresponding to a situation in which governments have no provision for flexibility, and the section is entitled “Rigid tariffs with Endogenous Political Pressure.” But in the first subsection (on p. 15) we are told that attention is restricted to the case of weak bindings throughout. Weak bindings seem to provide flexibility to apply lower tariffs, so they would not seem to be rigid tariffs, which makes the title to the section seem odd. Some additional clarity about terminology would be helpful here.
			\item On p. 17, I am not sure what τN in the third paragraph is. Do you have some specific pressure in mind that is suppressed? Or is this the tariff that is associated with eL? Or perhaps it was defined somewhere and I missed it. Similar remarks apply to expression (8) on p. 20. What is the definition of eN there? Is it different from eL?
			\item On p. 21, line 5, I don’t think you meant to say that the left hand side is decreasing in $\delta$, or maybe I am misunderstanding something.
		\end{itemize}
	\item Does costly state verification create threshold for endogenous $e$ even with verifiable shock conditionality?
	\item Differentiate from BS2005: they have exogenous only, so can't get my insight on 'free pass' on page 2; any paper that gets it with exogenous shocks only are fundamentally different
		\begin{itemize}
			\item I'm showing something new: that endogenizing politics in these models \textit{matters}
		\end{itemize}
	\item Is my write-up very different from the presentation? What are my main points?
	\item Clarify that it's not the $\gamma(e)$ that replaces Mitra / MRC inefficiencies; these are very complicated ways to get the government welfare function to be not everywhere increasing in lobbying effort.
		\begin{itemize}
			\item What I've done is provide a tractable way to get it
			\item May need to add more: Mitra 1999, Mitra 2002, Krishna and Mitra 2005
			\item Yes, relative to GH, mechanism by which greater lobbying activity leads government to give more weight to lobbying industry's profits is more of a black box. But GH functional form isn't very reasonable, and this is much better than what is usually done in the literature with exogenous shocks only. How would you put shocks into GH framework?
				\begin{itemize}
					\item Need to emphasize this being able to do shocks at same time as endogenous pressure
				\end{itemize}
		\end{itemize}
	\item Clarify that by long-run inefficiencies I also mean the lobbying inefficiencies of Mitra
	\item Do I really restrict attention to infinitely patient governments in Proposition 2?
\end{itemize}

@@
